SST_patterns

### 2020-01-20 SST_patterns.Rmd
boxplot

@@

#

    #Why are there no signals in 2011 in the SACTN data?
    # Why are some signals detected in the SACTN data? Is this because of the intensity of the signals?

# Reasons why upwelling might be detected at 10km rather than 50km
    # Dome in the isotherm blocking upwelling to reach the surface waters but does occur deeper down
# (Figures folder - ig 2 and figure 10)
```

>>>>

ggplot(data = Combined_frequency, aes(x = date, y = number_of_signals)) +
  geom_boxplot(aes(colour = product)) +
  theme(axis.text.x = element_text(angle = 90, hjust =1, vjust = 0.5))+
  #geom_smooth(aes(colour = product), method = "lm") +
  #labs(x = NULL) +
  facet_wrap(~site)

@@
